### 2023-10-25 generalExploration.Rmd
temporary silent some log, need to be solved ifor #3

            ##repro
           partner=population[[ind]]$partner
            repro=population[[ind]]$repro
            if(partner>0 & !repro){
                print(paste("childtest",ind,partner,population[[ind]]$community,population[[partner]]$community))
                population[[partner]]$repro=TRUE #make sure proba of reproduction is unique for all pair 
                ad_tr=initcomus$adaptivetraits[population[[ind]]$community,]
                lambda=b+r*sum(ad_tr)
                nchild=rpois(1,lambda)
                if(nchild>0){
                    for(i in 1:nchild){
                        print("newborn")
                        newborn=reproduction(population[[ind]],population[[partner]],neutraltraitsParam,population[[length(population)]]$id)
                        population[[newborn$id]]=newborn
                    }
                }
            }
            population[[ind]]$repro=FALSE

            ##marriage
            if(population[[ind]]$age>18 & population[[ind]]$partner <0){
                print("marriage attempt")
                if(runif(1)<m){
                    potential=sapply(population,function(i,s)if(i$age>18 & i$partner<0 & i$sex != s )return(i$id),s=population[[ind]]$sex)
                    potential=unlist(potential)
                    print(potential)
                    if(length(potential)>0){
                        if(length(potential)==1)partner=potential
                        else partner=sample(potential,1)
                        population[[ind]]$partner=partner
                        population[[partner]]$partner=ind
                        newcom=ifelse(runif(1)<rho,population[[ind]]$community,population[[partner]]$community)
                        population[[ind]]$community=population[[partner]]$community=newcom
                        print(paste("marriage",ind,partner,"moving all to",newcom,":",population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }

>>>>

            ##repro
           partner=population[[ind]]$partner
            canrepro=population[[ind]]$repro
            if(partner>0 & !canrepro){
                #print(paste("childtest",ind,partner,population[[ind]]$community,population[[partner]]$community))
                population[[partner]]$repro=TRUE #make sure proba of reproduction is unique for all pair 
                ad_tr=initcomus$adaptivetraits[population[[ind]]$community,]
                lambda=b+r*sum(ad_tr)
                nchild=rpois(1,lambda)
                if(nchild>0){
                    for(i in 1:nchild){
                        print("newborn")
                        newborn=reproduction(population[[ind]],population[[partner]],neutraltraitsParam,population[[length(population)]]$id)
                        population[[newborn$id]]=newborn
                    }
                }
            }
            population[[ind]]$repro=FALSE

            ##marriage
            if(population[[ind]]$age>18 & population[[ind]]$partner <0){
                #print("marriage attempt")
                if(runif(1)<m){
                    potential=sapply(population,function(i,s)if(i$age>18 & i$partner<0 & i$sex != s )return(i$id),s=population[[ind]]$sex)
                    potential=unlist(potential)
                    if(length(potential)>0){
                        if(length(potential)==1)partner=potential
                        else partner=sample(potential,1)
                        population[[ind]]$partner=partner
                        population[[partner]]$partner=ind
                        newcom=ifelse(runif(1)<rho,population[[ind]]$community,population[[partner]]$community)
                        population[[ind]]$community=population[[partner]]$community=newcom
                        print(paste("marriage",ind,partner,"moving all to",newcom,":",population[[partner]]$community,population[[ind]]$community))
                    }
                }
            }
